Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016

### 2019-04-19 draft-paper.Rmd
change repo name

This paper was produced using `RMarkdown` [@rmarkdown] and `knitr` [@knitr]. All corresponding code for this paper can be found in the github repository [github.com/jforbes14/journal-writing](https://github.com/jforbes14/journal-writing), and the data used is available in the `eechidna` package [@eechidna]. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.

>>>>

This paper was produced using `RMarkdown` [@rmarkdown] and `knitr` [@knitr]. All corresponding code for this paper can be found in the github repository [github.com/jforbes14/eechidna-paper](https://github.com/jforbes14/eechidna-paper), and the data used is available in the `eechidna` package [@eechidna]. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.

### 2019-04-19 draft-paper.tex
change repo name

This paper was produced using \texttt{RMarkdown} \autocite{rmarkdown} and \texttt{knitr} \autocite{knitr}. All corresponding code for this paper can be found in the github repository \href{https://github.com/jforbes14/journal-writing}{github.com/jforbes14/journal-writing}, and the data used is available in the \texttt{eechidna} package \autocite{eechidna}. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.

>>>>

This paper was produced using \texttt{RMarkdown} \autocite{rmarkdown} and \texttt{knitr} \autocite{knitr}. All corresponding code for this paper can be found in the github repository \href{https://github.com/jforbes14/eechidna-paper}{github.com/jforbes14/eechidna-paper}, and the data used is available in the \texttt{eechidna} package \autocite{eechidna}. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.
